\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-02-08 doc/publications/plos16/plos16.tex
add BMD table

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Features from the TCGA BRCA dataset ranked by their importance.}}
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
{\bf Variant} & {\bf Gene} & {\bf Importance}\\ \thickhline
x:xxxx & cell2 row 1 & cell3 row 1\\ \hline
x:xxxx & cell2 row 2 & cell3 row 2\\ \hline
x:xxxx & cell2 row 3 & cell3 row 3\\ \hline
\end{tabular}
\begin{flushleft} 
Here the importance is the Gini impurity measure when building a model using the cell type as the label.
\end{flushleft}
\label{featuretable}
%\end{adjustwidth}
\end{table}

>>>>

\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Features from the TCGA BRCA dataset ranked by their importance.}}
\begin{tabular}{|l|l|l|l|l|l|l|}
\hline
{\bf Variant} & {\bf Gene} & {\bf Importance}\\ \thickhline
8:120003727 & COLEC10 & 1.6393260970E-6\\ \hline
1:22702231  & ZBTB40  & 1.3901355155E-6\\ \hline
22:18923745 & PRODH   & 1.3769982791E-6\\ \hline
1:22702187  & ZBTB40  & 1.3350582926E-6\\ \hline
3:41111035  & CTNNB1  & 1.2707227479E-6\\ \hline
1:693731    &         & 1.1786957578E-6\\ \hline
1:22700351  & ZBTB40  & 1.1547011076E-6\\ \hline
8:120040181 & COLEC10 & 1.1511986773E-6\\ \hline
1:22701761  & ZBTB40  & 1.1495539020E-6\\ \hline
3:41120417  & CTNNB1  & 1.1325242379E-6\\ \hline
\end{tabular}
\begin{flushleft} 
The ten genes proximal to the top variants as ranked by their Gini impurity from a random forest model built on
individuals using high/low bone mineral density as the label.
\end{flushleft}
\label{featuretable}
%\end{adjustwidth}
\end{table}
